---
title: "Rioja Test Cases"
author: "Parismita Das"
date: "26 February 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Using Implemented Method

The inbuilt dataset RLGH(Diatom stratigraphic data) is used for showing clustering via constrained HAC method which is done by chclust function of Rioja Package.
In the code 
```
data(RLGH)
```

The distance Matrix is calculated by dist function of R, by default it calculates Euclidean Distance Metric
```
#diss is computed distance matrix of diatomic species relative abundance 
diss <- dist(sqrt(RLGH$spec/100))
```

Using chclust function for Constrained hierarchical clustering by coniss method, and comparing the dispersion of a hierarchical classification to that obtained from a broken stick model using bstick
```
clust <- chclust(diss)
```
bstick function compares the dispersion of a hierarchical classification to that obtained from a broken stick model. Hence plotting variances of ordination axes/components and overlaying broken stick distributions

```{r clustering, echo=FALSE}
source("implemented_method.R")

```

Plotting the dendogram diagram which we obtain after clustering, according to its distance.

```{r cluster, echo=FALSE}
source("cluster.R")

```

Showing the Clusters we get using using the function hclust.

Hence this shows the Hierarchical clustering using the Rioja Package
